Data_Import

### 2023-04-04 Data_Import.Rmd
Creating diagnosis variables, and initial visualization.

## Import data
Read in the dataset. 
```{r}
df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
#view(df)
Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
```
## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles

Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),

       #Lets make some new variables 
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
                              )))))
# Disorder subtypes 
# Mood Disorders
# Anxiety Disorders
# Obsessive Compusive Disorders
# Personality Disorders
# Substance Use Disorders
# Trauma related disorders
# Psychotic Disorders
# Eating Disorders

>>>>

## Import data
Read in the dataset. 
```{r}
df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
view(df)
Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS,SUMdep_0:SUManx_1,SUMdep_DC,SUManx_DC,BL_CUDOS, BL_CUXOS)
## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
view(Mothership)
Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
                              )))))
